\chapter{Methodologies}
% \graphicspath{{Chapter3/Figs/}{Chapter3/Figs/}}

Skizzieren der akademischen Methodik (kurz und projektbezogen) und der geplanten Vorgehensweise. Begründung der vorgesehenen Workflows, Hard- und Softwaretools. Definition von Phasen (Iterationen) mit Kontrollpunkten für Fortschritt, Feedback und Reflexion respektive die Weiterentwicklung. Möglicher Umfang: ca. 10-20%

\section{Participants}
\label{participants}

Forty-three patients of the psychiatric clinic with diagnosed major depression (12 male, Mage = 36.35, SDage = 7.92) participated in this study for monetary compensation (10 USD).

\section{Design}
\label{design}

- The study used a between-subject design (treatment group, control group) with the
depression score on the XXX depression scale as dependent variable.
- The study used a within-subject design (pre-treatment measurement, post-treatment
measurement) with the depression score on the XXX depression scale as dependent variable.
- The study used a mixed design with the between-subject factor group (treatment, control) and the within-subject factor time (pre-treatment, post-treatment). The depression score on the XXX depression scale served as the dependent variable.

\section{Materials}
\label{materials}

- Three types of materials were used. First,… Second,… Third,…

\section{Procedure}
\label{procedure}

- Before the experiment started, participants were randomly assigned to two groups: the X group and the Y group.
- The experiment consistent of two phases. In the first phase,….. . In the second phase,…. .
- The order of these two phases was counterbalanced
- First, participants had to… next… subsequently… finally…
- Simultaneously,…
- After participants finished X, they… % Example citation

\section{Data Analysis}
\label{data-analysis}

- First, they were randomly assigned to treatment and placebo group
- Both groups: 60 minutes intervention
- Treatment group: first,… next,…
- Placebo group: first, …next,…
- Finally, they filled out the depression questionnaire

\section{Goals}
\label{chapter3-goals}

o Did you describe everything that is needed to replicate your research?
o Did you cite the sources of your methods or paradigms?