\chapter{User interviews and outline}
\label{appendix3-user-interviews-and-outline}

This appendix chapter lists the outline and rough framework used to conduct the user interviews, as well as the notes taken by the author and IDUN’s product manager, Mark Melnykowycz, during the interview sessions. The notes are represented in the state they were in at the time of recording. The focus was on conducting user interviews especially in the Robbie and Evan personas, as they were the first actual users of the software platform targeted by the C-level management.

\section*{User interview outline for the Robbie persona}

Notion PDF export to be found in the file \textit{user\_interview\_with\_a\_robbie.pdf} in the appendices directory in the user interviews subdirectory.

\section*{User interview outline for the Evan persona}

Notion PDF export to be found in the file \textit{user\_interview\_with\_an\_evan.pdf} in the appendices directory in the user interviews subdirectory.

\section*{User interview with Paul Doyle}

Notion PDF export to be found in the file \textit{user\_interview\_with\_paul.pdf} in the appendices directory in the user interviews subdirectory.

\section*{User interview with Ghena Hammour}

Notion PDF export to be found in the file \textit{user\_interview\_with\_ghena.pdf} in the appendices directory in the user interviews subdirectory.

\section*{User interview with Nicole Zahnd}

Notion PDF export to be found in the file \textit{user\_interview\_with\_nicole.pdf} in the appendices directory in the user interviews subdirectory.

\section*{User interview with Melanie Baumgartner}

Notion PDF export to be found in the file \textit{user\_interview\_with\_melanie.pdf} in the appendices directory in the user interviews subdirectory.

\section*{User interview with Mayank Jain}

Notion PDF export to be found in the file \textit{user\_interview\_with\_mayank.pdf} in the appendices directory in the user interviews subdirectory.

\section*{User interview with Martin Hutchings}

Notion PDF export to be found in the file \textit{user\_interview\_with\_martin.pdf} in the appendices directory in the user interviews subdirectory.

\section*{User interview with Jacopo de Araujo}

Notion PDF export to be found in the file \textit{user\_interview\_with\_jacopo.pdf} in the appendices directory in the user interviews subdirectory.

\section*{User interview with Garrett Flynn}

Notion PDF export to be found in the file \textit{user\_interview\_with\_garrett.pdf} in the appendices directory in the user interviews subdirectory.

